Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-19 docs/manuscript/manuscript.tex
Third paragraph for clustering analysis.

>>>>

We compared Ward.D2, Ward.D, complete, and k-means algorithm methods to determine the best cuts, and also to confirm that Ward.D2 was the best clustering algorithm method to develop the deprogram tree. The 'NBClust' function was set to determine the best clustering methodology by choosing minimum clustering from 3 to max cuts of 7 and utilized all the indices.  The majority rule was implemented by the 'NBClust' function for Ward.d2, Ward.D, and the complete algorithm determined that the best clustering cut was four. However, k-means determined to be 3, but we determined that Ward.D2 is the best methodology thus far.

Next, we compared the best indicies values for different algorthim solving methodlogy to determine the best cuts to comfirm that Ward.D2 is the best methodlogy.
